\LaTeX\ Detecting Hand Direction for Computer Interaction

### 2014-12-08 paper/paper.tex
More doc.

@@

% TODO Insert image of HOG and VideoCap Image here

@@

\subsubsection{Performance of Different Classifiers}

\subsection{Evaluation as a Computer Interaction Device}

>>>>

\begin{figure*}
	\begin{center}
		%\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
		\includegraphics[height=140px]{figures/PointImage.png}
		\includegraphics[height=140px]{figures/PointHOG.png}
	\end{center}
	\caption{An image (on the left) and our corresponding HOG output (on the right). The location calculated by our algorithm is illustrated by the blue dot on the left image.}
	\label{fig:pointImages}
\end{figure*}

@@

@@

\subsubsection{Performance of Different Classifiers}
We evaluated the performance of both convolution neural networks and HOG with k-Nearest Neighbors and Linear Regression. The results from our tests our given in figure \ref{fig:hist}, which is a histogram of the error of the different classifiers. The error is the euclidean distance measured in pixels between the predicted point and the actual point.
\begin{figure*}
	\begin{center}
		%\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
		\includegraphics[width=0.9\linewidth]{figures/ClassifierErrorHist.png}
	\end{center}
	\caption{An image (on the left) and our corresponding HOG output (on the right). The location calculated by our algorithm is illustrated by the blue dot on the left image.}
	\label{fig:hist}
\end{figure*}
\subsection{Evaluation as a Computer Interaction Device}
